---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OmopIndices

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![CRAN status](https://www.r-pkg.org/badges/version/OmopIndices)](https://CRAN.R-project.org/package=OmopIndices)
[![R-CMD-check](https://github.com/OHDSI/OmopIndices/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/OHDSI/OmopIndices/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/OHDSI/OmopIndices/graph/badge.svg)](https://app.codecov.io/gh/OHDSI/OmopIndices)
<!-- badges: end -->

The goal of **OmopIndices** is to enable standardised and reproducible 
derivation of clinically and epidemiologically relevant patient-level indexes 
and covariates directly from OMOP CDM databases instances.

## Ecosystem

*OmopIndices* is part of the ecosystem of packages defined by 
[omopgenerics](https://darwin-eu.github.io/omopgenerics/). For more details on
the ecosystem you can read the [Tidy R programming with the OMOP Common Data Model](https://ohdsi.github.io/Tidy-R-programming-with-OMOP/)
book.

## Tested sources

| Source | Driver | CDM reference | Status |
|------------------|------------------|------------------|------------------|
| Local R dataframe | N/A | `omopgenerics::cdmFromTables()` | ![](https://img.shields.io/github/actions/workflow/status/OHDSI/OmopIndices/test-weekly.yaml?branch=main&job=local-omopgenerics) |
| In-memory duckdb datatabase | duckdb | `CDMConnector::cdmFromCon()` | ![](https://img.shields.io/github/actions/workflow/status/OHDSI/OmopIndices/test-weekly.yaml?branch=main&job=duckdb-CDMConnector) |

## Installation

You can install the CRAN version of OmopIndices as:

```{r, eval = FALSE}
install.packages("OmopIndices")
```

Or you can install the development version of OmopIndices from
[GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pkg_install("OHDSI/OmopIndices")
```

## Main functionality

OmopIndices adds patient-level measures to an existing `cdm_table`. Each
function returns the input table with one or more columns added, so functions
can be composed with the pipe operator. The input table must contain
`person_id` (or `subject_id`) and, for index-based measures, a `Date` column
that identifies the index date.

| Group | Functions | Output |
|---|---|---|
| Comorbidity and frailty | `addCharlsonIndex()`, `addUpdatedCharlsonIndex()`, `addElectronicFrailtyIndex()`, `addHospitalFrailtyRiskScore()` | Numeric score, optionally with a categorical column |
| Clinical covariates | `addBMI()`, `addPolypharmacyCount()` | BMI and maximum simultaneous ingredient count |
| Demographics | `addEthnicity()`, `addLocation()` | Person-level ethnicity and location fields |
| Socioeconomic status | `addSocioEconomicStatus()`, `addTownsend()`, `addIndexOfMultipleDeprivation()` | Townsend or IMD value |

The index functions use OMOP concepts from the supplied `conceptSet` to find
records in the requested window. When `conceptSet = NULL`, the package uses
the corresponding concept sets from `OmopConcepts` where available. A concept
set can also be supplied as a `codelist`, `codelist_with_details`, or
`concept_set_expression` object.

## Examples

### Mock data

For the purpose to illustrate the functionality of OmopIndices we will use the
*GiBleed* database contained by the [omock](https://ohdsi.github.io/omock/)
package.

```{r}
library(omock)
library(duckdb)
library(OmopIndices)

cdm <- mockCdmFromDataset(datasetName = "GiBleed", source = "duckdb")
```

### `addLocation()`

## A complete example

The following example derives several measures for a cohort. The default
index date is `cohort_start_date`; use `indexDate` to point to another date
column. Windows are expressed in days relative to the index date, so
`c(-365, 0)` means the year before and including the index date.

```{r, eval = FALSE}
library(dplyr)

cohort <- cdm$cohort |>
  addCharlsonIndex(ageAdjusted = TRUE) |>
  addElectronicFrailtyIndex() |>
  addHospitalFrailtyRiskScore() |>
  addBMI(window = c(-365, 0), order = "last") |>
  addPolypharmacyCount(window = c(-30, 0)) |>
  addEthnicity() |>
  addLocation()

cohort |>
  select(person_id, cohort_start_date, charlson_index, efi, hfrs, bmi,
         polypharmacy_count, ethnicity, location) |>
  glimpse()
```

## Choosing options

For reproducible analyses, specify the concept set and output names explicitly
when defaults do not match the study protocol. Index functions accept a named
`categories` list to add labelled categories alongside the score, for example:

```{r, eval = FALSE}
cohort <- cdm$cohort |>
  addHospitalFrailtyRiskScore(
    window = c(-365, 0),
    categories = list(
      low = c(0, 5),
      intermediate = c(5, 15),
      high = c(15, Inf)
    ),
    nameStyle = "hospital_frailty_risk"
  )
```

`addBMI()` can select the first, last, minimum, or maximum measurement in a
window. `addEthnicity()` and `addLocation()` try the values in `from`
sequentially, which makes it possible to provide fallbacks. Missing values
are filled with the corresponding `missing*Value` argument.

## Function reference

See the [reference site](https://ohdsi.github.io/OmopIndices/reference/) for
complete argument descriptions, accepted input types, and examples for every
exported function. The package is designed to work with local data frames and
database-backed OMOP CDM sources supported by `omopgenerics`.
