---
title: "OmopIndices default concepts"
output:
  rmarkdown::html_vignette:
    tabset: true
vignette: >
  %\VignetteIndexEntry{omop_indices_concepts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The core functions in **OmopIndices** add indexes to a table:

- `addCharlsonIndex()`
- `addUpdatedCharlsonIndex()`
- `addHospitalFrailtyRiskScore()`
- `addElectronicFrailtyIndex()`
- `addElectronicFrailtyIndex2()`

These indices depend on a set of codelists, these codelist can be provided by
the user using the `conceptSet` argument. If not provided the package contain
its own definition for each one of the codelist.

You can get the default codelists of a given index with `getIndexCodelist()`:

```{r}
library(OmopIndices)

getIndexCodelist("charlson")
```

You can explore the different codelists here:

```{r, echo=FALSE}
x <- OmopIndices:::concepts |>
  dplyr::group_by(.data$index) |>
  dplyr::group_split() |>
  as.list()
names(x) <- purrr::map_chr(x, \(xx) unique(xx$index))
x <- x |>
  purrr::map(\(xx) dplyr::select(xx, !"index"))

makeConceptSelector <- function(data, id) {
  concepts <- sort(unique(data$codelist_name))

  tables <- purrr::map(concepts, \(x) {
    tableId <- paste0(id, "-", x)
    display <- if (identical(x, concepts[[1]])) NULL else "none"

    htmltools::tags$div(
      id = tableId,
      class = "concept-table",
      style = if (is.null(display)) NULL else paste0("display:", display, ";"),
      visOmopResults::formatTable(
        data |>
          dplyr::filter(.data$codelist_name == .env$x) |>
          dplyr::select(!"codelist_name"),
        type = "gt"
      )
    )
  })

  htmltools::tags$div(
    id = id,
    class = "concept-selector",
    htmltools::tags$label(
      `for` = paste0(id, "-select"),
      "Choose a concept:"
    ),
    htmltools::tags$select(
      id = paste0(id, "-select"),
      class = "form-control",
      purrr::map(concepts, \(concept) {
        htmltools::tags$option(
          concept,
          value = concept,
          `data-target` = paste0(id, "-", concept)
        )
      })
    ),
    tables,
    htmltools::tags$script(htmltools::HTML(sprintf(
      "document.getElementById('%s-select').addEventListener('change', function() {
        document.querySelectorAll('#%s .concept-table').forEach(function(x) {
          x.style.display = 'none';
        });
        var target = this.options[this.selectedIndex].dataset.target;
        document.getElementById(target).style.display = 'block';
      });",
      id, id
    )))
  )
}
```

## Overview of codelists {.tabset}

### Charlson Index

```{r, echo=FALSE}
makeConceptSelector(x$charlson, "charlson")
```

### Updated Charlson Index

```{r, echo=FALSE}
makeConceptSelector(x$updatedCharlson, "updated-charlson")
```

### Hospital Frailty Risk Score

```{r, echo=FALSE}
makeConceptSelector(x$hfrs, "hfrs")
```

## {-}

## Diagnostics of codelists {.tabset}

You might want to perform diagnostics on the mapping of your source data and
assess how well the involved codelists are recorded you can easily do that using
**CodelistGenerator** or **PhenotypeR**.

### CodelistGenerator

```{r, eval=FALSE}
library(CodelistGenerator)
library(OmopIndices)
library(omock)

cdm <- mockCdmFromDataset(datasetName = "GiBleed", source = "duckdb")

codelist <- getIndexCodelist("charlson")

codeUse <- summariseCodeUse(x = codelist, cdm = cdm)

tableCodeUse(result = codeUse)
```

### PhenotypeR

```{r, eval=FALSE}
library(PhenotypeR)
library(CohortConstructor)
library(OmopIndices)
library(omock)

cdm <- mockCdmFromDataset(datasetName = "GiBleed", source = "duckdb")

codelist <- getIndexCodelist("charlson")

cdm$my_cohort <- conceptCohort(cdm = cdm, conceptSet = codelist, name = "my_cohort")

results <- phenotypeDiagnostics(cohort = cdm$my_cohort)

shinyDiagnostics(result = results, directory = getwd())
```

## {-}
