---
title: "OmopIndices default concepts"
output:
  rmarkdown::html_vignette:
    tabset: true
vignette: >
  %\VignetteIndexEntry{omop_indices_concepts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The core functions in **OmopIndices** add indexes to a table:

- `addCharlsonIndex()`
- `addUpdatedCharlsonIndex()`
- `addHospitalFrailtyRiskScore()`
- `addElectronicFrailtyIndex()`
- `addElectronicFrailtyIndex2()`

These indices depend on a set of codelists, these codelist can be provided by
the user using the `conceptSet` argument. If not provided the package contain
its own definition for each one of the codelist.

You can get the default codelists of a given index with `getIndexCodelist()`:

```{r}
library(OmopIndices)

getIndexCodelist("charlson")
```

You can explore the different codelists here:

```{r, echo=FALSE}
load(file = here::here("vignettes/articles/selectors.RData"))
```

## Overview of codelists {.tabset}

### Charlson Index

```{r, echo=FALSE}
selectorCharlson
```

### Updated Charlson Index

```{r, echo=FALSE}
selectorUpdatedCharlson
```

### Electronic Frailty Index

```{r, echo=FALSE}
selectorEFI
```

### Electronic Frailty Index 2

```{r, echo=FALSE}
selectorEFI2
```

### Hospital Frailty Risk Score

```{r, echo=FALSE}
selectorHFRS
```

## {-}

## Diagnostics of codelists {.tabset}

You might want to perform diagnostics on the mapping of your source data and
assess how well the involved codelists are recorded you can easily do that using
**CodelistGenerator** or **PhenotypeR**.

### CodelistGenerator

```{r, eval=FALSE}
library(CodelistGenerator)
library(OmopIndices)
library(omock)

cdm <- mockCdmFromDataset(datasetName = "GiBleed", source = "duckdb")

codelist <- getIndexCodelist("charlson")

codeUse <- summariseCodeUse(x = codelist, cdm = cdm)

tableCodeUse(result = codeUse)
```

### PhenotypeR

```{r, eval=FALSE}
library(PhenotypeR)
library(CohortConstructor)
library(OmopIndices)
library(omock)

cdm <- mockCdmFromDataset(datasetName = "GiBleed", source = "duckdb")

codelist <- getIndexCodelist("charlson")

cdm$my_cohort <- conceptCohort(cdm = cdm, conceptSet = codelist, name = "my_cohort")

results <- phenotypeDiagnostics(cohort = cdm$my_cohort)

shinyDiagnostics(result = results, directory = getwd())
```

## {-}
